### 2017-02-12 manuscript.rmd
cleaned up plot

	g_age =
		nodes_contrast %>%
		ggplot( aes( x=node_age, y=pic, col=Event ) ) + 
			geom_point( alpha=0.2 ) + 
			xlab( "Node age (millions of years)" ) + 
			ylab( "Phylogenetic independent \ncontrast" ) +
			ylim( 0, 0.3 ) +
			xlim( 0, 1000 ) +
			ggtitle( "(a)" ) +
			theme_classic()	+
			theme( legend.justification=c( 1, 1 ), legend.position=c( 1, 1 ) )

@@

	# Plot results of the ascertainment bias analyses

	label_age = str_c( "Wilcoxon p=", wilcox_filtered_age )

@@

	# Examine by expected variance (branch length)
	g_var_exp =
		nodes_contrast %>%
		ggplot( aes( x=var_exp, y=pic, col=Event ) ) + 
		geom_point( alpha=0.2 ) + 
		xlab( "Expected variance, \n depends mostly on branch length" ) + 
		ylab( "Phylogenetic independent \ncontrast" ) +
		ylim( 0, 0.3 ) +
		xlim( 0, 2000 ) +
		ggtitle( "(c)" ) +
		theme_classic()	+
		theme(legend.position="none")

	label_var = str_c( "Wilcoxon p=", wilcox_filtered_var )

>>>>

@@

	g_age =
		nodes_contrast %>%
		ggplot( aes( x=node_age, y=pic, col=Event ) ) + 
			geom_point( alpha=0.2, size = 0.5 ) + 
			xlab( "Node age (millions of years)" ) + 
			ylab( "Phylogenetic independent \ncontrast" ) +
			ylim( 0, 0.3 ) +
			xlim( 0, 1000 ) +
			ggtitle( "(a)" ) +
			theme_classic()	+
			guides( colour = guide_legend( override.aes = list( alpha = 1, size = 2 ) ) ) +
			theme( legend.justification=c( 1, 1 ), legend.position=c( 1, 1 ) )

	label_age = str_c( "Wilcoxon p=", signif( wilcox_filtered_age, 2 ) )

@@

	# Examine by expected variance (branch length)
	g_var_exp =
		nodes_contrast %>%
		ggplot( aes( x=var_exp, y=pic, col=Event ) ) + 
		geom_point( alpha=0.2, size = 0.5 ) + 
		xlab( "Expected variance, \n depends mostly on branch length" ) + 
		ylab( "Phylogenetic independent \ncontrast" ) +
		ylim( 0, 0.3 ) +
		xlim( 0, 2000 ) +
		ggtitle( "(c)" ) +
		theme_classic()	+
		theme(legend.position="none")

	label_var = str_c( "Wilcoxon p=", signif ( wilcox_filtered_var, 2 ) )
